Exploratory analysis using CopyKAT

### 2024-11-25 analyses/cell-type-wilms-tumor-06/supplemental-notebooks/compare-label-transfer-approaches.Rmd

- Label transfer code with Azimuth currently in `main` at commit `6af112d`. These results are referred to as `"azimuth"`.
- Label transfer code adapted from Azimuth. These results are referred to as `"adapted_azimuth"`.

@@

| Sample | Reference | Count | Azimuth | Azimuth-adapted |
|--------|-----------|-------|---------|-----------------|
| SCPSC000179 | L1 | 70 | Metanephritic cells | Intestinal epithelial cells | 
| SCPSC000179 | Organ | 64 | Kidney | Intestine | 
| SCPSC000179 | Organ | 20 | Lung | Kidney | 
| SCPSC000194 | L1 | 60 | Stromal cells | Mesangial cells | 
| SCPSC000194 | Organ | 35 | Kidney | Intestine | 
| SCPSC000194 | Organ | 36 | Lung | Kidney | 
| SCPSC000205 | Organ | 56 | Kidney | Intestine |
| SCPSC000208 | L1 | 101 | Mesangial cells | Metanephritic cells |  
| SCPSC000208 | L1 | 75 | Intestinal epithelial cells | Metanephritic cells |  
| SCPSC000208 | Organ | 149 | Kidney | Intestine |

@@

| Sample | Reference | Count | Azimuth | Azimuth-adapted |
|--------|-----------|-------|---------|-----------------|
| SCPSC000179 | cell type | 94 | mesenchymal cell | kidney epithelial cell | 
| SCPSC000205 | compartment  | 52 | fetal nephron |  stroma |

>>>>

- Label transfer code with Azimuth currently in `main` at commit `6af112d`. These results are referred to as `"azimuth"`.
- Label transfer code adapted from Azimuth at commit `3e2f90`. These results are referred to as `"adapted_azimuth"`.
- All code was run performed with the `2024-08-22` OpenScPCA data release.

@@

| Sample | Reference | Count | Azimuth | Azimuth-adapted |
|--------|-----------|-------|---------|-----------------|
| `SCPCS000179` | L1 | 70 | Metanephric cells | Intestinal epithelial cells |
| `SCPCS000179` | Organ | 64 | Kidney | Intestine |
| `SCPCS000179` | Organ | 20 | Lung | Kidney |
| `SCPCS000194` | L1 | 60 | Stromal cells | Mesangial cells |
| `SCPCS000194` | Organ | 35 | Kidney | Intestine |
| `SCPCS000194` | Organ | 36 | Lung | Kidney |
| `SCPCS000205` | Organ | 56 | Kidney | Intestine |
| `SCPCS000208` | L1 | 101 | Mesangial cells | Metanephric cells |
| `SCPCS000208` | L1 | 75 | Intestinal epithelial cells | Metanephric cells |
| `SCPCS000208` | Organ | 149 | Kidney | Intestine |

@@

| Sample | Reference | Count | Azimuth | Azimuth-adapted |
|--------|-----------|-------|---------|-----------------|
| `SCPCS000179` | cell type | 94 | mesenchymal cell | kidney epithelial cell |
| `SCPCS000205` | compartment  | 52 | fetal nephron |  stroma |

### 2024-11-25 analyses/cell-type-wilms-tumor-14/exploratory_analysis/03_cnv/03_copykat_SCPCL000850.Rmd

---
title: "Exploratory analysis using Copykat"
author: "Jingxuan Chen"
date: "`r Sys.Date()`"
output: html_document
---

@@

Here we test `CopyKat` to analyze the CNV profile for Wilms tumor sample (SCPCL000850), aiming to identify potential tumor cells from normal cells.

Before running this notebook, one should first generate `CopyKat` outputs as in `03_runCopyKat.R`.

@@

# The path to this module
path_anal <- file.path(path_repo,"analyses","cell-type-wilms-tumor-14") 
```

@@

```{r paths}
library_id <- "SCPCL000850"
scratch_out_dir <- file.path(path_anal, "scratch", "03_cnv","copykat")
dir.create(scratch_out_dir, showWarnings = FALSE, recursive = TRUE)
library_out_dir <- file.path(scratch_out_dir, library_id)
dir.create(library_out_dir, showWarnings = FALSE, recursive = TRUE)

## Input files
# load pre-processed sample objs & anchor transfer results
obj <- SeuratObject::LoadSeuratRds( file.path(path_anal,"scratch","00_preprocessing_rds",paste0(library_id,".rdsSeurat")) )
level <- "compartment"
predictions <- read.csv( file.path(path_anal, "results", "01_anchor_transfer_seurat", paste0(library_id, "_", level,".csv")) ) 
obj <- AddMetaData(object = obj, metadata = predictions)
copykat_result <- readr::read_rds( file = file.path(library_out_dir, paste0(library_id, "_copykat_resultobj.rds")) )
copykat_result_noref <- readr::read_rds( file = file.path(library_out_dir, paste0(library_id, "_noref_copykat_resultobj.rds")) )

```

@@

#### Run CopyKat with normal cells

@@

Plot CopyKat identifications onto UMAP.

@@

#### Run CopyKat without normal cells

Here, no normal cells were provided to CopyKat.

@@

In this Wilms tumor sample (SCPCL000850), it's likely that CopyKat is not working well: (i) The result with or without specifying normal cells are not consistent; (ii) From the heatmap, no much differences in CNV profile could be observed.

>>>>

---
title: "Exploratory analysis using CopyKAT"
author: "Jingxuan Chen"
date: "`r Sys.Date()`"
output: html_document
---

@@

Here we test `CopyKAT` to analyze the CNV profile for Wilms tumor sample (SCPCL000850), aiming to identify potential tumor cells from normal cells.

Before running this notebook, one should first generate `CopyKAT` outputs as in `03_run`CopyKAT`.R`.

@@

# The path to this module
path_anal <- file.path(path_repo, "analyses", "cell-type-wilms-tumor-14")
```

@@

```{r paths}
library_id <- "SCPCL000850"
scratch_out_dir <- file.path(path_anal, "scratch", "03_cnv", "copykat")
dir.create(scratch_out_dir, showWarnings = FALSE, recursive = TRUE)
library_out_dir <- file.path(scratch_out_dir, library_id)
dir.create(library_out_dir, showWarnings = FALSE, recursive = TRUE)

## Input files
# load pre-processed sample objs & anchor transfer results
obj <- SeuratObject::LoadSeuratRds(file.path(path_anal, "scratch", "00_preprocessing_rds", paste0(library_id, ".rdsSeurat")))
level <- "compartment"
predictions <- read.csv(file.path(path_anal, "results", "01_anchor_transfer_seurat", "RNA", paste0(library_id, "_", level, ".csv")))
obj <- AddMetaData(object = obj, metadata = predictions)
copykat_result <- readr::read_rds(file = file.path(library_out_dir, paste0(library_id, "_copykat_resultobj.rds")))
copykat_result_noref <- readr::read_rds(file = file.path(library_out_dir, paste0(library_id, "_noref_copykat_resultobj.rds")))
```

@@

#### Run CopyKAT with normal cells

@@

Plot `CopyKAT` identifications onto UMAP.

@@

#### Run CopyKAT without normal cells

Here, no normal cells were provided to `CopyKAT`.

@@

In this Wilms tumor sample (SCPCL000850), it's likely that `CopyKAT` is not working well: (i) The result with or without specifying normal cells are not consistent; (ii) From the heatmap, no much differences in CNV profile could be observed.
